---
title: "Basic Inferential Data Analysis"
author: "Amelia"
date: "2/12/2017"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE)
```

## Load Data and perform basic EDA


Basic EDA

```{r boxplot}
ggplot(data = ToothGrowth, aes(x=supp, y=len, fill=supp, group=supp)) + 
  geom_boxplot() + 
  facet_grid(~ dose) +
  ggtitle("Graph of Tooth Length against Dose Amount by Delivery Method") +
  labs(y="lenght of tooth")

```
Graph of Tooth Length against Dose Amount by Delivery Method



## Basic Summary of Data

The study investigates the effect of Vitamin C on tooth growth in Guinea Pigs. Based on the box plot, the length of tooth growth increases as the dosage increase for both orange juice and ascorbic acid.

## Compare tooth growth by supp and dose

Perform 2 sample t-test for different Delivery Method for 0.5mg/day
```{r ttest1}
# Perform 2 sample t-test 
## 0.5 dose
Tooth0.5 <- subset(ToothGrowth, dose==0.5)
t.test(data = Tooth0.5, len~supp,
       alternative = "two.sided",
       paired = FALSE, var.equal = FALSE,
       conf.level = 0.95)
```

The p-value is less than 0.05, we can reject the null hypothesis that delivery by orange juice and ascorbic acid for dosage of 0.5mg/day has no effect on tooth length.

Perform 2 sample t-test for different Delivery Method for 1mg/day
```{r ttest2}
## 1 dose
Tooth1 <- subset(ToothGrowth, dose==1)
t.test(data = Tooth1, len~supp,
       alternative = "two.sided",
       paired = FALSE, var.equal = FALSE,
       conf.level = 0.95)
```

The p-value is less than 0.05, we can reject the null hypothesis that delivery by orange juice and ascorbic acid for dosage of 1mg/day has no effect on tooth length.

Perform 2 sample t-test for different Delivery Method for 2mg/day
```{r ttest23}
## 2 dose
Tooth2 <- subset(ToothGrowth, dose==2)
t.test(data = Tooth2, len~supp,
       alternative = "two.sided",
       paired = FALSE, var.equal = FALSE,
       conf.level = 0.95)
```

The p-value is more than 0.05, we cannot reject the null hypothesis that delivery by orange juice and ascorbic acid for dosage of 2mg/day has no effect on tooth length.

## Conclusion
The tooth length is positively correlated to Vitamin C dosage for the doses studied (0.5, 1, 2mg/day) for both delivery method by orange juice and ascorbic acid.
Delivery by orange juice and ascorbic acid has effect on tooth length of guinea pigs in doses 0.5 and 1 mg/day, but no effect for 2mg/day. 

## Assumptions
1. Test subjects (Guinea Pigs) are on similar diets with no additional intake of vitamin C throught their daily diets (e.g.vegetables/fruits).
2. Test subjects randomly selected for the different treatments.

<br/>
<br/>
.




